Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2019-12-23 RET_Hosts.tex
Updates from Overleaf

The advancement of large-area, deep astronomical sky surveys in the past decade has led to a step change in the study of

@@

\begin{figure*}
\includegraphics[width=\textwidth]{figs/}
\caption{Star-forming galaxy main sequence.
\label{fig:sfms}}
\end{figure*}
\section{Analysis and results}
\label{sec:analysis} % used for referring to this section from elsewhere

>>>>

In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe). Since the turn of the century, observations of CCSNe have been supplemented by two rarer, more exotic transient classes. Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}. Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley1996a,Woosley1996b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.    and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g. \citealt{Quimby2011; Gal-Yam2012})

@@

\begin{figure*}
\includegraphics[width=0.5\textwidth]{figs/sSFR_Mike.png}
\caption{The sSFR of RET hosts, compared to CCSNe and the low-z SDSS sample.
\label{fig:sfms}}
\end{figure*}
\section{Analysis and results}
\label{sec:analysis} % used for referring to this section from elsewhere
